Market simulator

### 2020-10-09 analysis/05_market_simulator.Rmd
Testing the ability to import data to influence the defaults of the reactive table.

# Initial organization configuration
organization_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'organization_config01.csv')
)

@@

# Placeholder for organization reactive table
org_table <- as.data.frame(matrix(0, nrow = nrow(organization_data)))
# org_table <- reactive({read.csv(input$file_org$datapath)})

@@

# I think what we need to do to import data to fill this reactive element we need it look something like this

# org_table$org1_value[where (input$file_org == 1) and the corresponding level matches %in% org_table$levels] <- 1

@@

  # Organization 4
  org_table$org4_value <- 0
  org_table$org4_value[org_table$levels %in% input$org4_org] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
  org_table
})
```

@@

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_worship_attendance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})
```

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)

# Organization
selectInput(
  "org1_org",
  label = "Organization:",
  choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
  # selected = "Red Cross",
  selected = as.character(organization_data[1:4,][which(organization_data[1:4,2] == 1), 1]),
  width = "450px"
)

@@

# Follow international news
selectInput(
  "per3_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  # selected = "Always",
  elected = ifelse(
    sum(persona_data[4:5,4]) == 0, "Never",
    as.character(persona_data[4:5,][which(persona_data[4:5,4] == 1), 1])
  ),
  width = "450px"
)

@@

```{r import}
# Organization file input
fileInput(
  "file_org",
  "Import Organization Data"
)

# Persona file input
fileInput(
  "file_per",
  "Import Persona Data"
)

>>>>

# Initial organization configuration
organization_data <- read_csv(
  here::here('analysis', 'output', 'configurations', 'org_data_test1.csv')
)

org_update <- reactiveValues(data = NULL)
org_update$data <- organization_data

@@

@@

@@

  # Organization 4
  org_table$org4_value <- 0
  org_table$org4_value[org_table$levels %in% input$org4_org] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_issue] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_trans] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_fin_account] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_funding] <- 1
  org_table$org4_value[org_table$levels %in% input$org4_host_gov] <- 1
  org_table
})

@@

  # Persona 3
  per_table$per3_value <- 0
  per_table$per3_value[per_table$levels == 'Intercept'] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_national_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_international_news] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_news_medium] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_follow_gov] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_travel_developing] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_pref] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_institution_trust] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_others_charitable] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_worship_attendance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religion] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_charity_importance] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_trust_in_charity] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_donation_amount] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_12] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_volunteer_frequency] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_personal_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_family_activism] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_religious_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_sport_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_art_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_labor_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_political_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_environmental_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_professional_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_humanitarian_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_consumer_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_other_member] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_gender] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_marital_status] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_education] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_income] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_race] <- 1
  per_table$per3_value[per_table$levels %in% input$per3_age] <- 1
  per_table
})

per_update <- reactiveValues(data = NULL)
per_update$data <- per_table

@@

```{r org1-inputs}
# Naming
textInput(
  "org1_name",
  label = "Organization Name:",
  value = "Organization 1",
  placeholder = "Enter Organization Name",
  width = "450px"
)
# Organization
renderUI({
  selectInput(
    "org1_org",
    label = "Organization:",
    choice = c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross"),
    # selected = "Red Cross",
    selected = as.character(org_update$data[1:4,][which(org_update$data[1:4,2] == 1), 1]),
    width = "450px"
  )
})

@@

# Follow international news
selectInput(
  "per3_international_news",
  label = "Follow international news:",
  choices = c("Never", "Sometimes", "Always"),
  # selected = "Always",
  selected = ifelse(
    sum(persona_data[4:5,4]) == 0, "Never",
    as.character(persona_data[4:5,][which(persona_data[4:5,4] == 1), 1])
  ),
  width = "450px"
)

@@

```{r import}
# Organization file input
fileInput(
  "file_org",
  "Import Organization Data",
  accept = c("text/csv",
             "text/comma-separated-values,text/plain",
             ".csv")
)

actionButton(
  inputId = "org_apply",
  label = "Apply New Data",
  icon = icon("play")
)

observeEvent(eventExpr = input$org_apply, 
  handlerExpr = {
      req(input$file_org)
      file <- read_csv(input$file_org$datapath)
      org_update$data <- file
  }, ignoreNULL = FALSE)

# Persona file input
fileInput(
  "file_per",
  "Import Persona Data",
  accept = c("text/csv",
             "text/comma-separated-values,text/plain",
             ".csv")
)

# observeEvent(eventExpr = input$apply, 
#   handlerExpr = {
#       req(input$file_per)
#       file <- read_csv(input$file_per$datapath)
#       per_update$data <- file
#   }, ignoreNULL = FALSE)
